Computing Entropies With Nested Sampling

### 2017-06-28 paper/ms.tex
Results

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the depths
for $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of $L=0.001$
for $\tau$, $0.001\sqrt{101}$ for $\d$, and $0.001\sqrt{102}$ for
the joint run. The results were:
\begin{align}
\depth_{\tau}    &= 6.216  \pm 0.025 \\
\depth_{\d}      &= 480.13 \pm 0.32   \\
\depth_{\tau,\d} &= 479.96 \pm 0.31
\end{align}

To convert these to differential entropies, I added the log-volumes
for 1, 101, and 102 dimensions, which are
$-6.215$, $-557.252$, and $-562.746$ respectively. This gives
the following values for the differential entropies:
\begin{align}
H(\tau)     &=  0.001 \pm 0.025 \label{eqn:h_tau}\\
H(\d)       &= -77.12 \pm 0.32   \\
H(\tau, \d) &= -82.79 \pm 0.31   \label{eqn:h_joint}
\end{align}
The mutual information is equal to $H(\tau) + H(\d) - H(\tau, \d)$,
and can be computed from the results listed
in Equations~\ref{eqn:h_tau} to~\ref{eqn:h_joint}.
However, each of these three runs were produced with an identical random
seed for the reference points, so there is a way to reduce the uncertainty
by calculating $H(\tau) + H(\d) - H(\tau, \d)$ for each reference pair.
This is an instance of the
{\em common random numbers} technique of variance reduction.
The resulting  mutual information is
$I(\tau; \d) = 5.67 \pm 0.30$ nats.

>>>>

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the conditional entropy
$H(\tau | \d)$ using the algorithm with a tolerance of $L = 10^{-5}$.
The result was
\begin{align}
\depth &= 5.379 \pm 0.038
\end{align}
Converting to a differential entropy by adding $\ln (10^{-5})$, the conditional
entropy is
\begin{align}
H(\tau | \d) &= -5.441 \pm 0.038 \textnormal{ nats}.
\end{align}
Since the Uniform(0,1) prior has a differential entropy of zero, the
mutual information is $I(\tau; \d) = H(\tau) - H(\tau | \d) = 5.441 \pm 0.038$
nats.
